---
title: "Maine Farmers Market Price Report - Product Details"
output: html_document
params: 
    marketselect: NA
    daterange: NA
    prices: NA
    productlist: NA
    datause: NA
    empty: NA
---

```{r,include=FALSE}
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
cbPaletteL <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7","#808080","#E69F0050", "#56B4E950", "#009E7350", "#F0E44250", "#0072B250", "#D55E0050")
cbPalettet <- c("#99999950", "#E69F0050", "#56B4E950", "#009E7350", "#F0E44250", "#0072B250", "#D55E0050", "#CC79A750")
linetypelist <- c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20)


whatprices <- if(params$prices == 0){"both Organic and Conventional prices"} else {"only Organic prices" }
whichmarkets <- if(params$marketselect == "All"){"all three regions"} else {params$marketselect}
whichweek <- params$week
minweek <- min(params$daterange)
maxweek <- max(params$daterange)
```

# This report was generated on `r Sys.Date()`. 

# It includes data from `r whichmarkets` including `r whatprices` for the period between `r minweek` and `r maxweek`.  

```{r, echo = FALSE, message=FALSE, warning=FALSE}
  # Set up data
producttimedata <- params$datause %>% 
      filter(marketregion == params$marketselect | mr2 == params$marketselect) %>% 
      filter(weekdate >= min(params$daterange) & weekdate <= max(params$daterange)) %>%   
      filter(organic >= as.numeric(params$prices)) %>% 
      filter(Product %in% params$productlist) %>% 
      group_by(Product,`Week Starting`) %>% 
      summarize(`Average Price` = round(mean(price),2),
                `Minimum` = round(min(price),2),
                `Maximum` = round(max(price),2),
                `Number Reporting` = n())   

  # Make Plot
  producttimeplot <- producttimedata %>% 
       ggplot(aes(x=`Week Starting`,y=`Average Price`,color = Product,linetype=Product)) + geom_line(size=1.5) + geom_point()+
       scale_color_manual(values=cbPalette,name="Product") + scale_linetype_manual(values=linetypelist,name="Product") +
      scale_x_date(date_breaks = "1 week", date_labels = "%d-%b")
  producttimeplot

  # Make Table
    producttimetable <- producttimedata %>% 
      knitr::kable("html") %>%
      kable_styling("striped", full_width = F)
    producttimetable
```

---

This report is made possible with funding through the Maine Department of Agriculture, Conservation, and Forestry and the support of the Maine Federation of Farmers Markets, Maine Organic Farmers and Gardeners Association, Maine Farmland Trust, and the University of Maine.


